---
title: "AN597 Week 2- fshort"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Week 2 Homework Assignment - Frank Short

# Challenge 1.1
"First, create a vector of 1, word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

Then, extract every third element of this vector."

**First, I will use a function to subset the vector of 1 word character strings.**


```{r}
library(stringr)
v1<- c("Stately", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")
v1[seq(from = 3, to = 22, by = 3)]

```

# Challenge 1.2
"Take a look at the {stringr} package and the function str_split() to see if you can easily divide a single string into a vector of substrings."
Next, I will use the R package Stringr to extract every third word from one string. 

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
