---
title: "AN597 Week 2- fshort"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

####### LOOKS GREAT! WK

## R Week 2 Homework Assignment - Frank Short

# Challenge 1.1
"First, create a vector of 1, word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

Then, extract every third element of this vector."

**First, I will use a function to subset the vector of 1 word character strings.**


```{r challenge1.1}
library(stringr)
v1<- c("Stately", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")
v1[seq(from = 3, to = 22, by = 3)]

```

# Challenge 1.2
"Take a look at the {stringr} package and the function str_split() to see if you can easily divide a single string into a vector of substrings."
**Next, I will use the R package Stringr to extract every third word from one single string.** 

```{r challenge1.2}
library(stringr)
v2<-"Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
v2<-str_split(v2, " ", simplify = TRUE)
v2[seq(from = 3, to = 22, by = 3)]



```

# Challenge 2.1
"Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x"
```{r challenge2.1}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[,c(2,3,6)]
x

```
# Challenge 2.2 
"Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x"

```{r challenge2.2}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[6:8,]
x

```
# Challenge 2.3
"Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x"
```{r challenge2.3}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[2:6,2:9]
x

```
# Challenge 3
"Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)"

"Given this matrix, what would the following return?"
* a[1, 1, 1, 2]
```{r challenge3.1}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
a[1, 1, 1, 2]

```
* a[2, 3, 2, ]
```{r challenge3.2}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
a[2, 3, 2,]

```
* a[1:5, 1:5, 3, 3]
```{r challenge3.3}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
a[1:5, 1:5, 3, 3]

```
# Challenge 4
"Create a list representing this (simplified) primate taxonomy":
```{r challenge4.1}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae","Hylobatidae","Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini","Catarrhini")
Anthropoidea

Tarsioidea <- c("Tarsiidae")
Tarsioidea

Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Haplorhini

Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini

Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates

```
# Challenge 5
"Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE.

* Then, do the following:

+ Coerce the matrix to a data frame.

+ As a data frame, coerce the second column to be logical-valued

+ As a data frame, coerce the third column to be factor-valued

When you are done, use the str() command to show the data type for each variable in your dataframe."
```{r challenge5}
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
# Creating matrix with data entered row-wise. (See byrow = TRUE)
m3
# Coercing matrix to be data frame
m3 <- as.data.frame(m3)
colnames(m3)
# Coercing second column to be logical
m3[,2] <- as.logical(m3$V2)
# Coercing third column to be a factor
m3[,3] <- as.factor(m3$V3)
str(m3)

```
